---
title: The first notebook
---


# First section

Load some packages, do some analysis, generate some plots...

```{r setup}
library(ggplot2)
library(dplyr)
```

The following code block is hidden (code and results). 
Define a function to compute the fibonacci sequence. 
```{r include=FALSE}

# return the nth fibonacci number
fib_seq = function(n) {
  if(n < 1) stop("n must be pos. integer.")
  if (n == 1) {
    return(1)
  } else if (n == 2) {
    return(1)
  } else {
    f0 = 1
    f1 = 1
    for (i in 3:n) {
      tmp = f0 + f1
      f0 = f1
      f1 = tmp
    }
    return(f1)
  }
}
```

The following code block is hidden (hide code, show results). 

Show the first 10 fibonacci numbers:
```{r echo=FALSE}
lapply(1:10, fib_seq)
```


The following code block suppresses the results:
```{r results='hide'}
lapply(1:10, fib_seq)
```



# Summary
Every notebook should hava summary section that's understandable by biologists.
Include the 'highlights' here and repeat the corresponding figures.

```{r}
iris %>%
  ggplot(aes(x=Sepal.Length, y=Sepal.Width, color=Species)) + 
  geom_point() + 
  scale_color_brewer(type="qual", palette="Dark2")
```


